Liveness-Based Garbage Collection for Lazy Languages

### 2015-07-11 paper/paper.tex
Fixed minor naming issues

The process of liveness-based garbage collection involves going through 
each activation record on the stack and exploring each variable in the 
current activation record (root set). The liveness of each variable is 
determined using the program point and the variable name. The liveness 
of all variables are stored as DFAs. These DFAs are then encoded as a 
table. A variable is live only if an entry is found in this table.
All cells that are live are copied to the live semi-space. In case of 
\CONS\ cells the \CAR\ and \CDR\ pointers are chased and if they are 
live the copied \CONS\ cell will get the updated addresses of its 
\CAR\ and \CDR\ fields.

@@

\begin{table*}[ht!]
\caption{Comparing LGC with liveness for closures and reachability for closures}
\label{tab:compare-live-clo-reach-clo}
\centering
\begin{tabular}
{| l | r | r | r | r |}
\hline
Prog Name & Heap size & Num GC & Reachablity for closure & Liveness for closure \\ \hline
\verb@nqueens(8)@ & 10000 & 183 & 0.0087 & 0.2267\\ \hline
\verb@lambda@&10000&11&0.0010&4.9922\\ \hline
\verb@lcss@&10000&1&0.00008&34.6684\\ \hline
\end{tabular}
\end{table*}
To compare the  effect of using reachability to  copy closures instead
of liveness we take a couple  of programs from our benchmark suite and
execute       them      with       both.        As      shown       in
Table~\ref{tab:compare-live-clo-reach-clo},  the   number  of  garbage
collections in both cases are same but copying closures using liveness
takes a lot more time compared to reachability based copying.

>>>>

The process of liveness-based garbage collection involves going through 
each activation record on the stack and exploring each variable in the 
current activation record (root set). The liveness of each variable is 
determined using the program point and the variable name. The liveness 
of all variables are stored as DFA. These DFA are then encoded as a 
table. A variable is live only if an entry is found in this table.
All cells that are live are copied to the live semi-space. In case of 
\CONS\ cells the \CAR\ and \CDR\ pointers are chased and if they are 
live the copied \CONS\ cell will get the updated addresses of its 
\CAR\ and \CDR\ fields.

@@

\begin{table*}[ht!]
\caption{Comparing LGC times for different strategies}
\label{tab:compare-live-clo-reach-clo}
\centering
\begin{tabular}
{| l | r | r | r | r |}
\hline
Prog Name & Heap size & Num GC & Time taken using reachablity for closure  & Time taken using liveness for closure \\ \hline
\verb@nqueens(8)@ & 10000 & 183 & 0.0087s & 0.2267s\\ \hline
\verb@lambda@&10000&11&0.0010s&4.9922s\\ \hline
\verb@lcss@&10000&1&0.00008s&34.6684s\\ \hline
\end{tabular}
\end{table*}
To compare the  effect of using reachability to  copy closures instead
of liveness we take a couple  of programs from our benchmark suite and
execute       them      with       both.        As      shown       in
Table~\ref{tab:compare-live-clo-reach-clo},  the   number  of  garbage
collections in both cases are same but copying closures using liveness
takes a lot more time compared to reachability based copying.
